%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[10pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page


% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\setlength{\parskip}{1em}
% personal data
% personal data
\title{Software Engineer}
\firstname{Paulina}
\familyname{Silva}
\address{\color{black}}{\color{black}Vi\~na del Mar, Chile}
\email{pasilvagh@gmail.com}
\homepage{LinkedIn: https://cl.linkedin.com/pub/paulina-silva/61/115/908}   
\phone[mobile]{+56979010117}
\nopagenumbers{}

\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle


\section{Personal Information}
  \cvcomputer{\textbf{Name}}{Paulina Andrea Silva Ghio}{\textbf{Birthday}}{August 21, 1989}
  \cvcomputer{\textbf{R.U.T}}{17353242-3}{\textbf{Civil Status}}{Single}
  \cvcomputer{\textbf{Nationality}}{Chilean}{}{}
  \cvcomputer{\textbf{School}}{Scuola Italiana Arturo dell'Oro Valpara\'iso (2007)}{\textbf{College}}{Universidad T\'ecnica Federico Santa Mar\'ia, Valpara\'iso. Bachelor of Science (2013). Bachelor's Degree in Software Engineering (2015). Master in Software Engineering (currently).}%{\textbf{Estudios en paralelo}}{Magister en Ingenier\'ia Civ\'il Inform\'atica}

\section{Technical Summary}
    \cvcomputer{\textbf{Programming Languagues}}{C, C++,C\#, Java, Python, Bash}{\textbf{IDE}}{Eclipse, Microsoft Visual Studio 2008/2010/2012}
    \cvcomputer{\textbf{Web}}{HTML5, CSS3 and Javascript}{\textbf{Database}}{MySQL, PostgreSQL, SQL Server 2008}
    \cvcomputer{\textbf{Operating Systems}}{Linux, Windows 7/8}{\textbf{Object-Oriented Design}}{UML, Design Patterns, Misuse Patterns, Security Patterns}
    \vspace{1 mm}
    \textbf{Area of Study} \-\hspace{0.15cm}Software Development, Secure Software Architecture and Design, Distributed Systems, Computer Networking.

\section{Projects}
\textbf{TacPat4SS, FONDECYT}, (March 2015 - Today).
\begin{itemize}
	\item Area related: Software Engineering, Software Development, Secure Software Design and Architecture.
	\item Paper:``Software Development Initiatives to Identify and Mitigate Security Threats – A Systematic Mapping".
\end{itemize}
\vspace{3 mm}
\textbf{"Alpha Reality" - "Realidad Alfa" Project}, Videogame for Software Fair - "Feria de Software", sponsored by UTFSM (2011 - 2012).
\begin{itemize}
	\item Implementing \(C\#\) wrapper for Pattern Recognition (NyARToolKit) with XNA 4.0 Framework.
	\item Interface Design of the Videogame.
	\item Crafting of cards for recognition patterns
\end{itemize}

\section{Laboral Experience}
\cventry{Jan 2014 -- Mar 2014}{Software Developer (Intership)}{Mosaq Consultores Ltda,  San Sebasti\'an 2807 Of. 212. Las Condes, Santiago}{}{}{}
\cventry{Jan 2011 -- Mar 2011}{Software Developer (Intership)}{Software Development Team in UTFSM Graduate School Office}{}{}{}
\cventry{2008 -- 2015}{Class and Laboratory Assistant}{Courses: Informatics Foundation, Computer Networking, Management Systems. Laboratories: "Laboratorio de Computaci\'on" (DI UTFSM), "Laboratorio de Integraci\'on Tecnol\'ogica" (DI UTFSM). For more information see LinkedIn webpage (URL at top of this document)}{}{}{}
\cventry{2008 -- 2010}{Assistant in \textit{Ciclo de Charlas Inform\'aticas}}{"Departamento de Inform\'atica"}{}{}{}
\cventry{Octuber 2009}{Assistant}{Linux Conference sponsored by UTFSM (2009)}{}{}{}


\section{Skills}
\cvline{\textbf{Languages}}{Spanish (Native), English (Certificated by \textbf{TOEFL ITP} 2014), Japanese (Certificated by \textbf{Japanese Language Proficiency Test} 2013, level N4), Italian (Basic)}

%\section{LinkedIn}
%For more information please \href{https://cl.linkedin.com/pub/paulina-silva/61/115/908}{\textbf{click here}}.

\end{document}


%% end of file `template.tex'.

%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


